Visual Diagnostics of a Model Explainer

### 2019-03-26 papers/Visual Diagnostics of a Model Explainer/Visual Diagnostics of a Model Explainer Created by LIME.Rmd
worked on paper

- main objective of a model explainer: 
    - understand and explain model performance
- LIME does...
    - conceptually: models at two levels
        1. Simple = explainer model
        2. Complex = original "black box model"
    - usually: model predictions, maybe with ground truth
        - type I error
        - type II error
        - model is wrong in both cases
    - explanation is also a prediction
        - how reliable is that explanation?
          - we will present some tools that could help answer that question
          - we will show an example using this tools (bullet data)
          - we will mention some possible insights about LIME that these tools have shown us
            - explainer model generally has very low $R^2$ (probably due to binning)
            - "local" explanations are not local but are driven by the ("global") marginal distributions of covariates 
- Describe LIME including details on binning and linear regression in binned features and motivation for the binning

>>>>

Machine learning algorithms are have been proven to provide accurate predictions. However, this accuracy comes at a cost. With complicated algorithms, the ability to understand the mechanism in the data and the functional form of the model are lost. This has led for a push to be able to interpret machine learning algorithms. One approach to remedy this problem would be to develop a model explainer. The objective of such an explainer is to understand and explain model performance.

LIME (locally interpretable model explanations) is one such model explainer that was developed for this purpose (reference). Conceptually, LIME

- LIME does...
    - conceptually: models at two levels
        1. Simple = explainer model
        2. Complex = original "black box model"
    - usually: model predictions, maybe with ground truth
        - type I error
        - type II error
        - model is wrong in both cases
    - explanation is also a prediction
        - how reliable is that explanation?
          - we will present some tools that could help answer that question
          - we will show an example using this tools (bullet data)
          - we will mention some possible insights about LIME that these tools have shown us
            - explainer model generally has very low $R^2$ (probably due to binning)
            - "local" explanations are not local but are driven by the ("global") marginal distributions of covariates 
- Describe LIME including details on binning and linear regression in binned features and motivation for the binning
